\Large{Learning to Pivot with Adversarial Networks}

### 2016-11-01 tex/paper.tex
small things

Many inference problems involve data generation processes that are not uniquely
specified or are uncertain in some way. In a scientific context, the presence of
several plausible data generation processes is often associated to the presence
of systematic uncertainties. Robust inference is possible if it is based on a
pivot -- a quantity whose distribution is invariant to the unknown value of the
(categorical or continuous)
nuisance parameters that parametrizes this family of data generation processes. In
this work, we introduce a flexible adversarial training procedure to enforce the pivotal
property on a predictive model (e.g., a classifier), which allows one to tune the trade-off between
accuracy and robustness. We derive theoretical
results proving that the proposed procedure tends towards a minimax solution corresponding to a predictive model
that is both optimal and independent on the nuisance parameters, and demonstrate
its effectiveness  with a toy and physics examples.

>>>>

Many inference problems involve data generation processes that are not uniquely
specified or are uncertain in some way. In a scientific context, the presence of
several plausible data generation processes is often associated to the presence
of systematic uncertainties. Robust inference is possible if it is based on a
pivot -- a quantity whose distribution is invariant to the unknown value of the
(categorical or continuous)
nuisance parameters that parametrizes this family of generation processes. In
this work, we introduce a flexible training procedure based on adversarial networks to enforce the pivotal
property on a predictive model, which allows one to tune the trade-off between
accuracy and robustness. We derive theoretical
results showing that the proposed procedure tends towards a minimax solution corresponding to a predictive model
that is both optimal and independent on the nuisance parameters, and demonstrate
its effectiveness  with a toy and physics examples.
